The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-21 Background/history.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

% TODO: Change all domains to example.com
% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.

\textbf{Adam: This example is not correct, the STMP headers in listing 2 should have the "From" headers from the injection.}

When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well. 
\input{Background/smtpheaders}
%\input{Background/history_table}

>>>>

% TODO: Change all domains to example.com - DONE.
% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.

\begin{sloppypar}
When this code is given the malicious input \texttt{\lstinline{abc@example.com\\nCC:spc@example.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the equivalent SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well. 
\input{Background/smtpheaders}
%\input{Background/history_table}
\end{sloppypar}

### 2016-05-21 Background/py.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

# attack string => 
# 's@s.com\nBCC:spc@spc.com'
# for form["email"]

# to:s@s.com AND bcc:spc@spc.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

>>>>

# attack string => 
# 'abc@example.com\nBCC:spc@example.com'
# for form["email"]

# to:abc@example.com AND bcc:spc@example.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

### 2016-05-21 introduction.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

% TODO: Sai, can you add a reference to command injection vulnerabilities here?
Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting). Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.

\ehi vulnerabilities are a lesser-known command injection vulnerability. \ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}. This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby. With the proper injection string, \ehi vulnerabilities can be exploited by an attacker to inject additional headers, modify existing headers, or alter the contents of the \email---while still appearing to be from a legitimate source. \ehi exploits allow an attacker to perform \email spoofing, resulting in phishing attacks \emph{that are sent from the actual \email server}.

>>>>

% TODO: Sai, can you add a reference to command injection vulnerabilities here? DONE.
Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting). Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.

\ehi vulnerabilities are a lesser-known command injection vulnerability. \ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}. This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby. The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}. Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines). Some of these headers are mandatory (From, To, Date), but the headers could also include other information like the Subject, CC, BCC, etc.

\textbf{Sai: I believe that the discussion of SMTP Headers belongs here, before we say that E-Mail Header Injection can manipulate the headers. Do I need to include the message format as a listing? I think its superfluous, but let me know.}

With the proper injection string, \ehi vulnerabilities can be exploited by an attacker to inject additional headers, modify existing headers, or alter the contents of the \email---while still appearing to be from a legitimate source. \ehi exploits allow an attacker to perform \email spoofing, resulting in phishing attacks \emph{that are sent from the actual \email server}.
